Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-25 paper/ijcai/paper.tex
small fixes

\begin{abstract}
Several approaches have been proposed in the literature to reduce
debugging costs through automated software fault diagnosis.  Dynamic
Slicing (\ds{}) and Spectrum-based Fault Localization (\sfl{}) are
popular fault diagnosis techniques and normally seen as complementary.
This paper reports on a comprehensive study\comments{--using
  \numFaults{} documented software faults from a credible dataset--}
to reassess the effects of combining \ds{} with \sfl{}.  With this
combination, components that are often involved in failing but seldom
in passing test runs could be located and their suspiciousness
reduced. Results show that the \ds{}-\sfl{} combination, coined as
Tandem-SL, improves the diagnostic accuracy up to $73.7\%$
(\avgImprov\ on average). Furthermore, results indicate that the risk
of missing faulty statements, which \ds{}'s key limitation, is not
high---~\ds{} misses faulty statements in $9\%$\comments{($23$
  misses)} of the $\numFaults{}$ cases. To sum, we found that the
\ds{}-\sfl{} combination was practical and effective and encourage new
\sfl{} techniques to be evaluated against that optimization.
\end{abstract}

@@

The techniques we evaluate in this study are \combpar{k} and
SFL$^{k}$, which is the comparison baseline. \combpar{k} is as defined
in Section~\ref{sec:approach} (see Step 2 of the workflow) whereas
SFL$^{k}$ is as SFL, but it produces a ranking including exclusively
the statements from the best-$k$ ranked files.

@@

\begin{table}[H]
  \small
	\centering
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{lrr}
		\toprule
		Project             &  \multicolumn{1}{c}{$k=5$} & \multicolumn{1}{c}{$k=10$} \\ %\combpar{5}  & \combpar{10}
		\midrule

@@

\begin{table}[h!]
	\vspace{-0.2cm}
	\small
	\setlength{\tabcolsep}{3pt}
	\centering
\begin{tabular}{l|rr|rr}
		 \toprule
       & \multicolumn{2}{c|}{$k=5$} & \multicolumn{2}{c}{$k=10$} \\
		 Project        &   \sfl{}   & \comb &   \sfl{}   & \comb\\
		\midrule
		 \lang{}         &   84.6   & 100.0 & 84.6 & 96.9  \\
		\cmath{}           & 81.7 & 89.4 & 85.6 & 95.2 \\
		\chart{}           & {\cellcolor{Gray} 84.6} & {\cellcolor{Gray}76.9} & {\cellcolor{Gray}92.3} & {\cellcolor{Gray}84.6}\\
		\jtime{}           & 77.8 & 81.5 & 81.5 & 85.2\\
		\mockito{}           & 63.2 & 71.1 & 71.1 & 78.9\\   \midrule
		Total         & 79.6 & 87.3 & 83.5 & 91.2\\
		\bottomrule
	\end{tabular}
  \caption {Number of faults where at least one of the faulty-statements is in the \sfl{}$^{k}$ and \combpar{k} report}
  \label{table:fsws}
\vspace{-0.4cm}
\end{table}

@@

Figure~\ref{fig:boxplot} shows the $\Delta{}C$ distribution for each
variant in two different cases. On the left, we do not consider the
test engineering problems and faults of omission ($227$ faults). The two negative
outliers present the cases where the buggy-class was not in the top
$k$. On the right, we only consider the cases where at least one
of the variants resulted in an increase of $\Delta{}C$ ($116$ faults), i.e., the
cases where \ds{} improves \sfl. Although, we observe
a considerable amount of cases where $\Delta{}C$ is negative or zero in Figure~\ref{fig:diagnosis}, we also see that there is a considerable amount of faults which could benefit a lot with \combpar{k}, in Figure~\ref{fig:boxplot}.
\begin{figure}[h]
		\vspace{-0.2cm}
		\centering
		\includegraphics[width=0.49\textwidth]{figures/boxplot.pdf}
		\vspace{-0.6cm}

		\caption{Distribution of $\Delta{}C$ per variant when not considering
		test engineering problems and fault of omissions (left) and only considering
		the cases where \combpar{k} achieved improvement under one of
      the variants (right)}
		\label{fig:boxplot}
		\vspace{-0.2cm}

\end{figure}

@@

\begin{table}[h!]
	\tiny
	\centering
	\setlength{\tabcolsep}{3pt}
	\begin{tabular}{@{}c|c|c|c|c@{}}
\toprule
  & SFL$^{5}$      & SFL$^{10}$     & \combpar{5}              & \combpar{10}              \\ \midrule
Mean  & \textbf{590.7} (584.3)   &  \textbf{512.7} (516.4)  & \textbf{573.4} (679.7)  & \textbf{506.6} (614.0)   \\ \midrule
Median & \textbf{46.5} (49.4)    & \textbf{54.5} (53.0) & \textbf{42.7} (69.3)  & \textbf{40.0} (56.9)\\ \midrule
Variance & \textbf{1257.0} (1223.1)  &  \textbf{1171.5} (1148.1) & \textbf{1239.1} (1352.4) &  \textbf{1167.0} (1294.9) \\ \midrule
Shapiro-Wilk &\makecell{$W$ = 0.52 \\ $p$ = 1.75 x $10^{-24}$} & \makecell{$W$ = 0.48 \\ $p$ = 2.50 x $10^{-25}$} & \makecell{$W$ = 0.51 \\ $p$ = 1.10 x $10^{-24}$} & \makecell{$W$ = 0.48 \\ $p$ = 2.26 x $10^{-25}$}  \\ \midrule
Friedman & \multicolumn{4}{c}{\makecell{$\chi^{2}$ = 162.61 \\ p-value = 5.00 x $10^{-35}$}} \\
\bottomrule
\end{tabular}
  \caption {Statistical tests for $C$}
  \label{table:st}
\end{table}

>>>>

\begin{abstract}
Several approaches have been proposed in the literature to reduce
debugging costs through automated software fault diagnosis.  Dynamic
Slicing (\ds{}) and Spectrum-based Fault Localization (\sfl{}) are
popular fault diagnosis techniques and normally seen as complementary.
This paper reports on a comprehensive study\comments{--using
  \numFaults{} documented software faults from a credible dataset--}
to reassess the effects of combining \ds{} with \sfl{}.  With this
combination, components that are often involved in failing but seldom
in passing test runs could be located and their suspiciousness
reduced. Results show that the \ds{}-\sfl{} combination, coined as
Tandem-SL, improves the diagnostic accuracy up to $73.7\%$
(\avgImprov\ on average). Furthermore, results indicate that the risk
of missing faulty statements, which is a \ds{}'s key limitation, is not
high---~\ds{} misses faulty statements in $9\%$\comments{($23$
  misses)} of the $\numFaults{}$ cases. To sum, we found that the
\ds{}-\sfl{} combination was practical and effective and encourage new
\sfl{} techniques to be evaluated against that optimization.
\end{abstract}

@@

The techniques we evaluate in this study are \combpar{k} and
SFL$^{k}$, which is the comparison baseline. \combpar{k} is as defined
in Section~\ref{sec:approach} (see Step $2$ of the workflow) whereas
SFL$^{k}$ is as SFL, but it produces a ranking including exclusively
the statements from the best-$k$ ranked files.

@@

@@

\begin{table}[h]
	\vspace{-0.2cm}
	\small
	\setlength{\tabcolsep}{3pt}
	\centering
\begin{tabular}{l|rr|rr}
		 \toprule
       & \multicolumn{2}{c|}{$k=5$} & \multicolumn{2}{c}{$k=10$} \\
		 Project        &   \sfl{}   & \comb &   \sfl{}   & \comb\\
		\midrule
		 \lang{}         &   84.6   & 100.0 & 84.6 & 96.9  \\
		\cmath{}           & 81.7 & 89.4 & 85.6 & 95.2 \\
		\chart{}           & {\cellcolor{Gray} 84.6} & {\cellcolor{Gray}76.9} & {\cellcolor{Gray}92.3} & {\cellcolor{Gray}84.6}\\
		\jtime{}           & 77.8 & 81.5 & 81.5 & 85.2\\
		\mockito{}           & 63.2 & 71.1 & 71.1 & 78.9\\   \midrule
		Total         & 79.6 & 87.3 & 83.5 & 91.2\\
		\bottomrule
	\end{tabular}
  \caption {Number of faults where at least one of the faulty-statements is in the \sfl{}$^{k}$ and \combpar{k} report}
  \label{table:fsws}
\vspace{-0.4cm}
\end{table}

@@

Figure~\ref{fig:boxplot} shows the $\Delta{}C$ distribution for each
variant in two different cases. On the left, we do not consider the
test engineering problems and faults of omission ($227$ faults). The two negative
outliers present the cases where the buggy-class was not in the top
$k$. On the right, we only consider the cases where at least one
of the variants resulted in an increase of $\Delta{}C$ ($116$ faults), i.e., the
cases where \ds{} improves \sfl. Although, we observe
a considerable amount of cases where $\Delta{}C$ is negative or zero in 
Figure~\ref{fig:diagnosis}, we also see that there is a considerable amount 
of faults which could benefit a lot with \combpar{k}, in Figure~\ref{fig:boxplot}.

\begin{figure}[h]
		\vspace{-0.2cm}
		\centering
		\includegraphics[width=0.49\textwidth]{figures/boxplot.pdf}
		\vspace{-0.6cm}

		\caption{Distribution of $\Delta{}C$ per variant when not considering
		test engineering problems and fault of omissions (left) and only considering
		the cases where \combpar{k} achieved improvement under one of
      the variants (right)}
		\label{fig:boxplot}
		\vspace{-0.2cm}
\end{figure}

@@

\begin{table}[h]
	\tiny
	\centering
	\setlength{\tabcolsep}{3pt}
	\begin{tabular}{@{}c|c|c|c|c@{}}
\toprule
  & SFL$^{5}$      & SFL$^{10}$     & \combpar{5}              & \combpar{10}              \\ \midrule
Mean  & \textbf{590.7} (584.3)   &  \textbf{512.7} (516.4)  & \textbf{573.4} (679.7)  & \textbf{506.6} (614.0)   \\ \midrule
Median & \textbf{46.5} (49.4)    & \textbf{54.5} (53.0) & \textbf{42.7} (69.3)  & \textbf{40.0} (56.9)\\ \midrule
Variance & \textbf{1257.0} (1223.1)  &  \textbf{1171.5} (1148.1) & \textbf{1239.1} (1352.4) &  \textbf{1167.0} (1294.9) \\ \midrule
Shapiro-Wilk &\makecell{$W$ = 0.52 \\ $p$ = 1.75 x $10^{-24}$} & \makecell{$W$ = 0.48 \\ $p$ = 2.50 x $10^{-25}$} & \makecell{$W$ = 0.51 \\ $p$ = 1.10 x $10^{-24}$} & \makecell{$W$ = 0.48 \\ $p$ = 2.26 x $10^{-25}$}  \\ \midrule
Friedman & \multicolumn{4}{c}{\makecell{$\chi^{2}$ = 162.61 \\ p-value = 5.00 x $10^{-35}$}} \\
\bottomrule
\end{tabular}
  \caption {Statistical tests for $C$}
  \label{table:st}
\end{table}
